---
---
---

# Compare Dissimilarity of Manifestos

First, we extract the manifestos for four countries: Greece, Italy, Ireland and Sweden under specified three timestamps.

```{r message=FALSE, warning=FALSE}
# install.packages("manifestoR")
# install.packages("textTinyR")
library(textTinyR)
library(manifestoR)
library(tidyverse)
library(tm)

# import api key
mp_setapikey("manifesto_apikey.txt")

# call function to access required corpus
corpus_ir_1st <- mp_corpus(countryname == "Ireland" & edate > as.Date("2007-05-01") & edate < as.Date("2007-05-31"))
corpus_ir_2nd <- mp_corpus(countryname == "Ireland" & edate > as.Date("2011-02-01") & edate < as.Date("2011-02-28"))
corpus_ir_3rd <- mp_corpus(countryname == "Ireland" & edate > as.Date("2016-02-01") & edate < as.Date("2016-02-29"))

corpus_swe_1st <- mp_corpus(countryname == "Sweden" & edate > as.Date("2006-09-01") & edate < as.Date("2006-09-30"))
corpus_swe_2nd <- mp_corpus(countryname == "Sweden" & edate > as.Date("2010-01-01") & edate < as.Date("2010-09-30"))
corpus_swe_3rd <- mp_corpus(countryname == "Sweden" & edate > as.Date("2018-09-01") & edate < as.Date("2018-09-30"))

corpus_gre_1st <- mp_corpus(countryname == "Greece" & edate > as.Date("2007-09-01") & edate < as.Date("2007-09-30"))
corpus_gre_2nd <- mp_corpus(countryname == "Greece" & edate > as.Date("2009-10-01") & edate < as.Date("2009-10-31"))
corpus_gre_3rd <- mp_corpus(countryname == "Greece" & edate > as.Date("2015-09-01") & edate < as.Date("2015-09-30"))

corpus_it_1st <- mp_corpus(countryname == "Italy" & edate > as.Date("2006-04-01") & edate < as.Date("2006-04-30"))
corpus_it_2nd <- mp_corpus(countryname == "Italy" & edate > as.Date("2013-02-01") & edate < as.Date("2013-02-28"))
corpus_it_3rd <- mp_corpus(countryname == "Italy" & edate > as.Date("2018-03-01") & edate < as.Date("2018-03-31"))


```

Then we flatten each tm corpus to form a single character string and perform the following text processing:

1.  remove punctuations
2.  remove line breaks
3.  remove digits
4.  remove stop words of corresponding languages
5.  perform stemming based on the corresponding language

Then we calculate the cosine distance between corpus.

```{r message=FALSE, warning=FALSE}
library(SnowballC)

# a function to process a corpus for consine distance calculation

preprocess <- function(corpus, stop_words_lang, stem_lang) {
  all_text <- sapply(corpus, as.character)
  single_doc <- paste(all_text, collapse = " ")
  single_doc <- tolower(single_doc)
  single_doc <- gsub("[[:punct:]]", "", single_doc)
  single_doc <- gsub("\n", "", single_doc)
  single_doc <- gsub("\\d", "", single_doc)
  single_doc <- removeWords(single_doc, stopwords::stopwords(stop_words_lang))
  words <- unlist(strsplit(single_doc, "\\s+"))
  stemmed <- wordStem(words, language = stem_lang)
  single_doc <- paste(stemmed, collapse = " ")
  return(single_doc)
}

ir_1 <- preprocess(corpus_ir_1st, "english", "en")
ir_2 <- preprocess(corpus_ir_2nd, "english", "en")
ir_3 <- preprocess(corpus_ir_3rd, "english", "en")

swe_1 <- preprocess(corpus_swe_1st, "swedish", "swedish")
swe_2 <- preprocess(corpus_swe_2nd, "swedish", "swedish")
swe_3 <- preprocess(corpus_swe_3rd, "swedish", "swedish")

gre_1 <- preprocess(corpus_gre_1st, "greek", "greek")
gre_2 <- preprocess(corpus_gre_2nd, "greek", "greek")
gre_3 <- preprocess(corpus_gre_3rd, "greek", "greek")

ita_1 <- preprocess(corpus_it_1st, "italian", "italian")
ita_2 <- preprocess(corpus_it_2nd, "italian", "italian")
ita_3 <- preprocess(corpus_it_3rd, "italian", "italian")

ir_1_2 <- cosine_distance(ir_1, ir_2)
ir_2_3 <- cosine_distance(ir_2, ir_3)

swe_1_2 <- cosine_distance(swe_1, swe_2)
swe_2_3 <- cosine_distance(swe_2, swe_3)

gre_1_2 <- cosine_distance(gre_1, gre_2)
gre_2_3 <- cosine_distance(gre_2, gre_3)

ita_1_2 <- cosine_distance(ita_1, ita_2)
ita_2_3 <- cosine_distance(ita_2, ita_3)
```

We store the result in a data frame and visualise the result.

```{r warning=FALSE}
library(tidyverse)
# Create a dataframe
df <- tibble(
  Country = c("Ireland", "Italy", "Sweden"),
  ManifestoDisimilarityOne = c(ir_1_2, ita_1_2, swe_1_2),
  ManifestoDisimilarityTwo = c(ir_2_3, ita_2_3, swe_2_3)
)

df <- df |> pivot_longer(cols = -Country, names_to = "ManifestoTimeStamp", values_to = "DisimilarityValue")
```

```{r warning=FALSE}
ggplot(df, aes(x = ManifestoTimeStamp, y = DisimilarityValue, fill = Country)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  labs(title = "Manifesto Disimilarity Across Three TimeStamps in 4 European Countries",
       x = "Time Stamps for Manifestos",
       y = "Dissimilarity Value") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12))

```

A cosine distance between two corpus measures the similarity based on the cosine of the angle between the two corpus vectors.

Cosine distance ranges from 0 to 1, with 0 indicating that the two corpus are perfectly similar and 1 indicating that the two corpus are perfectly dissimilar. Lower cosine distance suggests higher similarity and higher cosine distance suggests greater dissimilarity.

The data indicates notable shifts in the political manifestos of both Ireland and Sweden following the euro crisis. Unfortunately, the analysis for Italy is incomplete for the initial timestamp due to the absence of corpus data. Subsequent to the refugee crisis, both Ireland and Sweden display consistent levels of dissimilarity, suggesting a maintained divergence in their political manifestos from the earlier period. Once the data for Italy becomes accessible at the second timestamp, there is a discernible dissimilarity in its political manifestos as well, aligning with the trends observed in the other two countries and our assumptions.
